---
title: "Grab bag topics"
author: "Ravi Brenner"
date: "2024-12-03"
output: github_document
---

## To handle PHI

-   Create a folder for the PHI in an entirely separate location from the project/git repository

-   create a symbolic link in your git repo to the external folder, e.g. using "ln -s PATH NAME" in terminal

-   Also add that folder to .gitignore, just to be safe

Dropbox is a separate story...will sync automatically...so good to avoid if using PHI

## Using projectr package 

(From Professor Goldsmith)

Use projectr::proj_start(proj_path, proj_data_path) to set up default folders, default .gitignore file, readme, etc.

Could be useful! Especially for PHI use, it automatically sets up the data folder being somewhere else.

`cabinets` package by nt-williams is another cool option https://github.com/nt-williams/cabinets

## The `here` package

`here` keeps track of where files are, with subfolders etc. by telling R to always start from the project directory location, and go down from there.

(I've used this before, can be finicky if not using a .Rproj but it works well and keeps things organized).

## Always use regression

t.test example
```{r}
with(mtcars, t.test(mpg[am == 0], mpg[am == 1])) |>
  broom::tidy()
```

Same as this
```{r}
t.test(mpg ~ am, data = mtcars) |>
  broom::tidy()
```

But these are the same as using `lm`
```{r}
lm(mpg ~ am, data = mtcars) |>
  broom::tidy()
```

(also see this article for more https://lindeloev.github.io/tests-as-linear/)

## LLMs in data science

Once Github copilot is activated, you can use it to complete code.

(Need to log in to account and potentially pay for this service also).

Potentially a helpful option to speed things up, especially as chatbots improve over time.

Can also upload files to ChatGPT, and ask it to do the data manipulation and stuff for you.

